% !TEX root = ../main.tex
\documentclass[../main.tex]{subfiles}
\begin{document}
Multi-component modelling of complex galaxies is a valuable tool in the quantitative understanding of galaxy evolution, however it is plagued by issues with convergence, model selection and parameter degeneracies, which either limits it to simple models for large samples, or complex models in very small samples (summarize as ``quality or quantity"). This paper presents a novel framework, built inside the Zooniverse citizen science platform, which enables volunteers to help crowdsource the creation of multiple component photometric models of galaxies from FITS images. We test if this method can help solve the quandry over choosing ``quality" or ``quantity" for complex galaxy image modelling.

We have run the method (including a final algorithmic optimization from the best crowd-sourced solution) on a sample of 296 images from the Sloan Digital Sky Survey (SDSS). The results from these data demonstrate that using citizen science to make selections on number of model parameters to include, as well as in some parameters identifying best fits, is a promising technique for modeling the images of complex galaxies. We examine the robustness of this new method to variation in number and population of citizen scientists, as well as compare it to automated fitting pipelines. We demonstrate that it is possible to consistently recover accurate models which show good agreement with, or improve on previous models in the literature. These results will be used in future work to investigate spiral arm formation mechanisms and we release our catalogue of models to the community.
\end{document}
